\LARGE \bf Enriching Robot's Actions with Affective Movements

### 2017-06-11 RO-MAN-2017-2/Parts/RelatedWork.tex
Reviewed

The use of emotion enrichment to improve human robot interaction is not new. There have been several researchers that have enhanced their social robots with emotions or studied how to convey emotions in robotic platforms~\cite{Li2011,Brown2014}. One of the first, well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions. This platform uses a specific set of movements based on the Ekman's studies on human emotion expression~\cite{Ekman2004}. Other approaches have tried to use anthropomorphic~\cite{Arras2012} and human-like platforms to convey emotions to study the response of people towards the robot. However, the emotions portrayed were hand-coded, hard-wired to the respective platforms, and their parametrization is not available.

@@

Other works in performance robotics have developed systems that do not convey any kind of emotion as \textit{Roboscopie}~\cite{Roboscopie2012}, Fan and collaborators~\cite{Fan2009}, and adaptation of Shakespeare's  Midsummer Night's Dream~\cite{murphy2011} use robots in performances with real actors, but without any emotional expression. Although these works have expressed emotions in their studies, they did not focus on creating a framework that could be used by other researchers in HRI. Therefore, the use of affective architectures for virtual agents (e.g. SAIBA/BML framework~\cite{Kopp2006}) could be though as a feasible solution. However, these frameworks describe high level actions without giving relevant details to its implementation in physical platforms. This gap cannot be filled by making a direct mapping between the abstract actions and the physical platforms. This is due to the fact that virtual agents do not have physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007,Canamero2010}.

>>>>

The use of emotion enrichment to improve human robot interaction is not new. There have been several researchers that have enhanced their social robots with emotions or studied how to convey emotions in robotic platforms~\cite{Li2011,Brown2014}. One of the first, well-known expressive robots is Kismet~\cite{Breazeal2002}, a robotic face able to interact with people and to show emotions. This platform uses a specific set of movements based on the Ekman's studies on human emotion expression~\cite{Ekman2004}. Other approaches have tried to use anthropomorphic platforms~\cite{Arras2012} to convey emotions to study the response of people towards the robot. However, the emotions portrayed were hand-coded, hard-wired to the respective platforms, and their parametrization is not available.

@@

Other works in performance robotics have developed systems that do not convey any kind of emotion as \textit{Roboscopie}~\cite{Roboscopie2012}, Fan and collaborators~\cite{Fan2009}, and adaptation of Shakespeare's  Midsummer Night's Dream~\cite{murphy2011} use robots in performances with real actors, but without any emotional expression. Although these works have expressed emotions in their studies, they did not focus on creating a framework that could be used by other researchers in HRI. The use of affective architectures for virtual agents (e.g., SAIBA/BML framework~\cite{Kopp2006}) could be thought as a feasible solution. However, these frameworks describe high level actions without giving relevant details to its implementation in physical platforms. This gap cannot be filled by making a direct mapping between the abstract actions and the physical platforms. This is due to the fact that virtual agents do not have physical constraints, while robots are constrained by their physical capabilities~\cite{Saerbeck2007,Canamero2010}.
